### 2022-08-07 chapters/optimization/python-dir/python_interperters.tex
add : dendogram

\section{placeholder}
we performed a shapiro normality test for the first on the results, and almost all the p-values smaller than alpha=0.01\%
therefore the distrubution is not normal - which is kinda true because if it was normal then we dont have any comparaison --

@@

\begin{figure}
    \caption{energy consumption of different impelementations using Bit Operation benchmarks (Joule) }
    \label{table:bitops}
    \begin{tabular}{lrrrrr}
        \toprule
        benchmark    & A          & GG         & LL         & Or         & XOR        \\
        \midrule
        activepython & 676.980672 & 763.208040 & 651.783048 & 743.016425 & 728.828481 \\
        cpython2     & 441.082298 & 435.886950 & 430.846171 & 415.247383 & 419.081447 \\
        cpython3     & 595.209019 & 685.085315 & 563.839300 & 657.972734 & 655.560574 \\
        cython       & 35.077408  & 182.688395 & 274.177830 & 34.868014  & 34.504778  \\
        nuitka       & 33.260991  & 32.980380  & 33.256450  & 33.472770  & 33.030889  \\
        numba2       & 9.102939   & 8.411176   & 9.460620   & 9.375920   & 9.755952   \\
        numba3       & 9.566646   & 10.144212  & 9.219703   & 9.344613   & 9.665108   \\
        pypy2        & 8.456867   & 7.844918   & 8.286278   & 8.138692   & 7.952999   \\
        pypy3        & 7.552731   & 8.093884   & 8.108508   & 8.669448   & 8.623737   \\
        shedskin     & 8.024198   & 8.070870   & 8.399917   & 8.126236   & 8.277546   \\
        \bottomrule
    \end{tabular}

\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{imgs/barplot_binarry_tree}
    \caption{energy behaviour based on multiprocessing}
    \label{fig:python_multiprocessing}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{imgs/bitopts_mean}
    \caption{Mean consumption of different implementations of bit operations (Joule) }
    \label{fig:bitops}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{imgs/alltomti_performance}
    \caption{different interpererts optimisation }
    \label{fig:tommi_all}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{imgs/tommti_compare__pypy2_pypy3}
    \caption{green factor of pypy }
    \label{fig:pypy2vspypy3}
\end{figure}

@@

for the other interpeters pypy is very promising especially when it comes to data maniupulation as one can see in the figure \ref{fig:bar_tommti_vector}
pypy is by far the best interperer when it comes to treating vectors.
numba2 introduced the JIT but wasn't as promising as numba3.

>>>>

\section{placeholder}
we performed a shapiro normality test for the first on the results, and almost all the p-values smaller than alpha=0.01\% therefore the distrubution is not normal

@@

\begin{figure}

    \label{table:bitops}
    \begin{tabular}{|lrrrrr|}
        \toprule
        benchmark    & A          & GG         & LL         & Or         & XOR        \\
        \midrule
        activepython & 676.980672 & 763.208040 & 651.783048 & 743.016425 & 728.828481 \\
        cpython2     & 441.082298 & 435.886950 & 430.846171 & 415.247383 & 419.081447 \\
        cpython3     & 595.209019 & 685.085315 & 563.839300 & 657.972734 & 655.560574 \\
        cython       & 35.077408  & 182.688395 & 274.177830 & 34.868014  & 34.504778  \\
        nuitka       & 33.260991  & 32.980380  & 33.256450  & 33.472770  & 33.030889  \\
        numba2       & 9.102939   & 8.411176   & 9.460620   & 9.375920   & 9.755952   \\
        numba3       & 9.566646   & 10.144212  & 9.219703   & 9.344613   & 9.665108   \\
        pypy2        & 8.456867   & 7.844918   & 8.286278   & 8.138692   & 7.952999   \\
        pypy3        & 7.552731   & 8.093884   & 8.108508   & 8.669448   & 8.623737   \\
        shedskin     & 8.024198   & 8.070870   & 8.399917   & 8.126236   & 8.277546   \\
        \bottomrule
    \end{tabular}
    \vfill
    \centering
    \includegraphics[width=\linewidth]{imgs/bitopts_mean}
    \caption{energy consumption of different impelementations using Bit Operation benchmarks (Joule) }
\end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=\linewidth]{imgs/barplot_binarry_tree}
%     \caption{energy behaviour of different python implementations for the binarry Tree benchmark}
%     \label{fig:binarrytree}
% \end{figure}

\begin{figure}

\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{imgs/dendogram_interpreters}
    \caption{Dendogram of the different implementations}
    \label{fig:dendogram}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{imgs/alltomti_performance}
    \caption{different interpererts optimisation }
    \label{fig:tommi_all}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{imgs/tommti_compare__pypy2_pypy3}
    \caption{green factor of pypy }
    \label{fig:pypy2vspypy3}
\end{figure}

@@

for the other interpeters pypy is very promising especially when it comes to data maniupulation as one can see in the figure \ref{fig:bar_tommtei_vector}
pypy is by far the best interperer when it comes to treating vectors.
numba2 introduced the JIT but wasn't as promising as numba3.
